---
title: "Untitled"
output: html_document
---

# Conceptual

1. TV and radio are significant and predictive for number sold while newspaper
is not significant indicated by the low p-value.

2. KNN regression is based on a distance in variable space while KNN classifer
is based on a plurality of nearest neighbor classifications.

3a.
i. Incorrect, B3 is > 0 indicating there is a positive effect
from college since College takes the value of 1 for the dummy variable.

ii. Correct above..

3b.
```{r}
earnings <- function(gpa, iq, level) {
    return (50 + 20 * gpa + 0.07 * iq + 35 *
    level + 0.01 * iq * gpa - 10 * gpa * level)
}
print(earnings(4.0, 110, 1))
```

Earnings = 137.1

3c. The effect may be small in some cases but without a t-test it is difficult
to assess

4a. I would epxect the RSS of the cubic fit to be smaller because it contains the
true linear fit and has additional coefficients that likely lessen the observed
error due to measurement randomness.

4b. I would expet the test RSS of the linear fit to be better.

4c. We do not know

4d. dont know

5.

8. 
```{r}
library(ISLR)
attach(Auto)

mpg_fit <- lm(mpg ~ horsepower)
summary(mpg_fit)
```
a. yes
b. P-value of <2e-16
c. negative
d.
```{r}
predict(mpg_fit, data.frame(horsepower=c(98)), interval="confidence")
predict(mpg_fit, data.frame(horsepower=c(98)), interval="prediction")
```

9.
a.
```{r.plot}
pairs(Auto)
```
b.
```{r}
cor(Auto[, -which(names(Auto) == "name")])
```
c.
```{r}
limited = Auto[, -which(names(Auto) == "name")]
auto.fit = lm(mpg ~ ., data=limited)
summary(auto.fit)
```

11.
a. 
```{r}
set.seed(1)
x <- rnorm(100)
y <- 2 * x + rnorm(100)
fit <- lm(y~x + 0)
summary(fit)
```
b.
```{r}
set.seed(1)
x <- rnorm(100)
y <- 2 * x + rnorm(100)
fit <- lm(x~y + 0)
summary(fit)
```
c.

14.
```{r}
set.seed (1)
x1 <- runif (100)
x2 <- 0.5 * x1 + rnorm (100) / 10
y <- 2 + 2 * x1 + 0.3 * x2 + rnorm (100)
fit <- lm(y ~ x1 + x2)
summary(fit)
```
b.
```{r}
plot(x1, x2)
```

```{r}
fit <- lm(y ~ x1)
summary(fit)
```

```{r}
fit <- lm(y ~ x2)
summary(fit)
```